An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-02-11 EconGrowth.Rnw
Now doing all covariance tables in one knitr chunk.

<<Covariance_Table_US, results='asis'>>=
printCovarTable("US")
@

<<Covariance_Table_UK, results='asis'>>=
printCovarTable("UK")
@

<<Covariance_Table_JP, results='asis'>>=
printCovarTable("JP")
@

<<Covariance_Table_CN, results='asis'>>=
printCovarTable("CN")
@

<<Covariance_Table_ZA, results='asis'>>=
printCovarTable("ZA")
@

<<Covariance_Table_SA, results='asis'>>=
printCovarTable("SA")
@

<<Covariance_Table_IR, results='asis'>>=
printCovarTable("IR")
@

<<Covariance_Table_TZ, results='asis'>>=
printCovarTable("TZ")
@

<<Covariance_Table_ZM, results='asis'>>=
printCovarTable("ZM")
@

>>>>

<<Print_Covariance_Tables, results='asis'>>=
printCovarTable("US")
printCovarTable("UK")
printCovarTable("JP")
printCovarTable("CN")
printCovarTable("ZA")
printCovarTable("SA")
printCovarTable("IR")
printCovarTable("TZ")
printCovarTable("ZM")
@
